Algorithmic and Economic Aspects of the Internet

### 2012-12-03 report/paper.tex
El report
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

\subsection{1 v 1 tests}
Given these initially dismal results, we decided that a good place to start a
detailed analysis would be a 1v1 test with the Giveaway trader, which is
clearly the worst of all the traders within the BSE system. 300 1v1 tests were
performed, we used the same schedule as the many versus many test. Results
where both bots made zero profit were eliminated, this brought the number of
tests included for analysis down from 300 to 242. Of these tests 103 were won
by Giveaway and 139 were won by our agent. The distributions of profit for each
agent, as well as the distribution of differences in profit can be seen in the
following histograms.

@@

In order to conduct this test we represented each run as a pair of
$(profit_{giveaway}, profit_{agent})$. The profits in the pair are taken from
the average profit column in the output of running BSE, so in fact the profit
values are divided by two, because their are two of each agent running in the
system. This will not effect the output of the test, as the change in magnitude
is the same for both agents. The test runs over the difference between the
first and second value in the pair. Our null hypothesis $H0$ is that the median
difference of each pair is zero, with our positive hypothesis $H1$ being that
the median difference of each pair is not zero. We performed the test using
scipy's built in Wilcoxon signed-rank test implementation\cite{scipy:wilcoxon}
and the results were extremely conclusive.  With $p=1.2\times10^{-6}$ we reject
$H0$ and conclude that the difference in medians is significant, as such the
profits generated by our agent are significantly better than Giveaway's.

This test was repeated for each of ZIC, Shaver, Sniper and ZIP. In each case
the results were that our bot performed significantly worse than the other agent (p < 0.01
in each case).

\subsection{One in many tests}
We also evaluated the agent initially in a one versus many test against a ZIC
trader which gave better results. Using a similar strategy above we started
with 25 tests to determine winners and average profits, however the results
were not totally conclusive, so we decided to generate some 300 experimental
results in order to attempt to draw conclusions about whether the bot performs
better in one v many tests. The results are shown below, using the same supply
and demand schedule, and two of our agent (1 buyer, 1 seller) and 20 of
the other agent (10 buyers, 10 sellers):

\begin{center}
\begin{tabular}{ l|l|l|l }
Agent Type & Tests lost & $\Delta$ Profit Mean & $\Delta$ Profit StDev \\
\hline
Giveaway & 157 & -2.28 & 86.95\\ 
ZIC & 225 & 52.86 & 83.99\\ 
Shaver & 287 & 76.36 & 46.06\\ 
Sniper & 256 & 19.49 & 16.74\\ 
ZIP & 234 & 64.76 & 89.76
\end{tabular}
\end{center}

We can see here that the agent performs better when trading on it's own than in
a small swarm.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

and don't forget to end the environment with
{figure*}, not {figure}!

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The acm\_proc\_article-sp document class file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}

>>>>

\subsection{1 v 1 tests} Given these initially dismal results, we decided that
a good place to start a detailed analysis would be a 1v1 test with the Giveaway
trader, which is clearly the worst of all the traders within the BSE system.
300 1v1 tests were performed, we used the same schedule as the many versus many
test, with a longer total trading time of 1800. Results where both bots made
zero profit were eliminated, this brought the number of tests included for
analysis down from 300 to 242. Of these tests 103 were won by Giveaway and 139
were won by our agent. The distributions of profit for each agent, as well as
the distribution of differences in profit can be seen in figures 2 and 3.

@@

In order to conduct this test we represented each run as a pair of
$(profit_{giveaway}, profit_{agent})$. The profits in the pair are taken from
the average profit column in the output of running BSE. This means that in
reality the profit values are divided through by two for each agent, as it is
the average of 1 seller and 1 buyer in each case. This does not affect the test
because the change in magnitude is the same for both agents.

The test runs over the difference between the first and second value in the
pair. Our null hypothesis $H0$ is that the median difference of each pair is
zero, with our positive hypothesis $H1$ being that the median difference of
each pair is not zero. We performed the test using scipy's built in Wilcoxon
signed-rank test implementation\cite{scipy:wilcoxon} and the results were
conclusive.  With $p=1.2\times10^{-6}$ we reject $H0$ and conclude
that the difference in medians is significant, as such the difference in
profits generated is statistically significant.

This test was repeated for each of ZIC, Shaver, Sniper and ZIP. In each case,
the results were that, our agent performed worse than the other
agent with our agent having a lower median score and the Wilcoxon test giving
p < 0.01 in each case.

In light of the test against Giveaway it is  worth noting the spike at a profit
of around ~4000 in figure 3.  These occasions correspond to Giveaway making
4000 more profit than our agent. A quick analysis of the data indicates that
nearly all of these occur when our agent issues no trades (zero balance at the
end of trading). As such we concluded that for whatever reason on these events
(96/242 runs) the conditions never reach the point where our agent starts
trading. This is not unreasonable given the warmup period of the algorithm and
the low number of traders in the system.

\subsection{Experiments with supply and demand schedules}

We wanted to determine under what, if any, supply and demand conditions our
agent could outperform some of the better algorithms in the system. In order to
do this we conducted several experiments with varying supply and demand
schedules listed below. We use n=300 as our number of trials, 1 v 1 tests and a
total time period length of 1800. Initially all tests were performed against
ZIC

\subsection{Totally open market}

In this set of trials we used the hard limits of BSE, minimum price of 1 and
maximum price of 1000 for both the supply and demand curves, for the entire
time range, using a drip-poisson timemode with a 30 second replenishment time.
The idea behind this experiment is to gather an understanding as to how our
agent performs in a totally unconstrained environment.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
\end{document}
